Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-03-23 analysis/paper/shceof.Rmd
Saca lineas al pedo
Elimina chunk innecesario

```{r corr-eofs}

background_palette <- grDevices::colorRampPalette(c("white", scales::muted("red")),
                                                  space = "Lab")
# 
# eof_naive[, eof[[1]]$left, by = lev] %>% 
#   .[, item := paste(lev, EOF, sep = "_")] %>% 
#   widyr::pairwise_cor(item, time, hgt) %>% 
#   setDT() %>%
#   # .[]
#   .[tstrsplit(item1, "_")[[1]] != tstrsplit(item2, "_")[[1]], ] %>% 
#   .[tstrsplit(item1, "_")[[1]] != 50] %>% 
#   .[, item1 := tstrsplit(item1, "_")[[2]]] %>%
#   .[, item2 := tstrsplit(item2, "_")[[2]]] %>% 
#   .[, r2 := round(correlation^2, 2)] %>% 
#   dcast(item1 ~ item2, value.var = "r2") %>% 
#   setnames("item1", "200 hPa") %>% 
#   kbl2(booktabs = TRUE, caption = "$R^2$ between pairs of EOFs of each level rounded to two decimals.") %>% 
#   # add_header_above(c("", "50 hPa" = 4)) %>% 
#   column_spec2(2:5,  background = spec_color2(.table[[.col]], option = background_palette, 
#                                               scale_from = c(0, 1)),
#                color = ifelse(.table[[.col]] > .5, "white", "black")) %>% 
#   add_header_above(c("", "50 hPa" = 4)) %>%
#   kable_classic()
```

@@

(ref:pp-temp-cap-1) Same as Figure \@ref(fig:pp-temp-2) but for cEOF1.

>>>>

@@

(ref:pp-temp-cap-1) Same as Figure \@ref(fig:pp-temp-2) but for cEOF1.
(ref:pp-temp-cap-1) Same as Figure \@ref(fig:pp-temp-2) but for cEOF1.
